---
title: "MTG_Project_Dataviz"
author: "Alexandre Francony"
date: "2023-01-12"
output: 
  rmdformats::readthedown:
    highlight: kate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Cleanning the data

Delete any line that has a cardSet in Unstable, Unhinged, Unglued, Unsanctioned or Unfinity (these editions are irrelevant in our case), then write the new dataset in a new csv file.
**(ONLY ONCE!)**
```{r}
MTGcsv <- read.csv("./MTG_data/MTGcards.csv")
mtg_data <- as.data.frame(MTGcsv)

mtg_data <- mtg_data[mtg_data$cardSet != "Unstable",]
mtg_data <- mtg_data[mtg_data$cardSet != "Unhinged",]
mtg_data <- mtg_data[mtg_data$cardSet != "Unglued",]
mtg_data <- mtg_data[mtg_data$cardSet != "Unsanctioned",]
mtg_data <- mtg_data[mtg_data$cardSet != "Unfinity",]

write.csv(mtg_data, file = "./MTG_data/MTGcards_clean.csv")
```

## Importing the cleaned data

Let's import the new csv file and create a new dataframe, then we can see the first 5 cards.
```{r}
mtg_data <- read.csv("./MTG_data/MTGcards_clean.csv")
mtg_data <- as.data.frame(mtg_data)
```

Show an overview (summary) of the dataset
```{r}
summary(mtg_data)
```

Show an overview of the 5 first cards (cardName, cardType, manaCost, convertedMana, cardSet, rarity)
```{r}
mtg_data[1:5, c("cardName", "cardType", "manaCost", "convertedMana", "cardSet", "rarity")]
```
